\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\begin{document}
	
	
\chapter{Common Dependencies}

\section{Python Core}
\begin{itemize}
\item Numpy
\item Scipy
\item Statsmodels
\item Sci-Kit Learn
\item TensorFlow
\item Keras
\end{itemize}


\begin{section}{Visualization - Optional?}
\begin{itemize}
\item MatPlotLib
\item Bokeh
\item Seaborn
\end{itemize}
\end{section}


\section{Third Party}

\begin{itemize}
\item CUDA Development toolkit (available through Anaconda?)
\item numba
\item ArrayFire?
\item MAGMA?
\item MKL
\end{itemize}







\chapter{Included External Packages}

\section{Banpei}

Anomaly detection using Singular Spectrum Transformation and Hotelling -- the bindings for these have been placed in ./anomalies/*.



\section{Context Anomaly Detector}
Not really sure how this works... are there examples or more documentation somewhere?


\section{Donut}
Anomaly detection model built around tensorflow and keras. Not sure what the best way to integrate this will be?



\section{Luminol}
Luminol has what looks like a lot of pretty robust / automatic anomaly detection algorithms -- does a bunch of tests/checks automatically and sees what comes back.\\

Seems a bit complicated to get into (their models expect a special time series class), but would definitely be worth fully integrating. 



\begin{section}{Nupic}
	content...
\end{section}

\begin{section}{Prophet}
	adsf	
\end{section}

\begin{section}{Pwlf}
	asdf
\end{section}

\section{StatsModels Time Series Analysis}

statsmodels.tsa has a lot of good stuff, not for clustering or segmenting, but regression, change point detection, probably a lot of other things too



\begin{section}{PyBasicBayes}
	content...
\end{section}

\begin{section}{PyFlux}
	adsf	
\end{section}

\begin{section}{PhHSMM}
	asdf
\end{section}

\begin{section}{Robust PCA}
Small package which implements Robust Principal Component Analysis. The bindings for this have been placed in ./encoding/RPCA.py.
\end{section}


\begin{section}{Ruptures}
	content...
\end{section}

\begin{section}{Saxpy}
	adsf	
\end{section}

\begin{section}{Seglearn}
	asdf
\end{section}


\begin{section}{Simple Segment}
	content...
\end{section}

\begin{section}{Sci-kit Learn}
	adsf	
\end{section}

\begin{section}{Skyline}
	asdf
\end{section}


\begin{section}{SPARCWave}
	content...
\end{section}

\begin{section}{Telemanom}
	adsf	
\end{section}

\begin{section}{TICC}
	asdf
\end{section}

\begin{section}{tslearn}
	content...
\end{section}


	
	
\end{document}